A community-maintained standard library of population genetic models

### 2020-05-13 response-to-reviewers.md

Dear Graham and the Editorial Board of *eLife*,

Please find attached our revised manuscript entitled, 
"A community maintained standard library of population genetic models"
for consideration for publication.

We thank you and the reviewers of our manuscript for your enthusiasm for our project
and the constructive criticisms that you have raised. As you will find below, we have tried
our level-best to incorporate all of the changes suggested in the reviews. 
While that is so, in a few places we have decided that suggested changes were beyond
the scope of the current manuscript and leave them for future work.

What follows below is a point-by-point response to the comments.

@@

# Editors comments

> 1) Ensuring that the language about the models & parameters conveys the correct sense of uncertainty. Obviously the reviewers and the authors know that these just represent best guesses at the moment, but as this platform catches on we don't want these numbers & models to be seen as gospel.

We fully agree that the language in the original manuscript was not careful enough in conveying uncertainty about the models and parameters we discuss.
We have made edited the text throughout the manuscript to address this.
See our response to Reviewer 1 below for examples.
We have also added a bit more to the discussion (below "next steps") on this point.

@@

> 2) We would like to see the SLIM integration demonstrated with an application that msprime doesn't cover. This could be, for example, a figure of the average value some summary statistics surrounding a selective under the human demographic model. The reviewers didn't want this to be a lot of work, e.g., it would be outside of the scope of the current paper to demonstrate the power of a range of selection methods. However, we felt that a simple demonstration of the functionality would substantially increase the scenarios easily available and imaginable by readers of the paper.

We would like to see this also and agree that it would be of great interest.
However, we felt that performing adequate simulations with selection would require
a substantial amount of additional work and would significantly expand the scope of
the manuscript.
Furthermore, discussing selection would distract from the current relatively simple focus
on inference of demographic history.
We definitely intend to include selection (and expand the available generic models) in future work,
as we now discuss in greater detail in the Discussion ("next steps").

Instead, we have decided to add an a section validating the use of SLiM in stdpopsim neutral simulations (see "simulation engines" section in the results and Supplementary Figures S1 and S2).
Our focus there was to show that under neutral simulations, SLiM produced data that were consistent with the coalescent simulations of msprime.
To expand on this fundamental point, we also examined the influence of population size down-scaling, which is a common practice used in forward simulations, and indeed often crucial for tractable compute times.
While this is by no means a comprehensive investigation into this issue, we do believe that it demonstrates the use of SLiM in future applications that will also simulate selection.

@@

> 3) We felt that the discussion would benefit from a discussion of the details not yet incorporated into the platform, e.g. sex-specific recombination, gene conversion, assembly error, structural variants etc. Such an addition might spur future development, and also give the authors an opportunity to discuss general ways forward on these issues.

Thank you for this good idea -
we have expanded the section of the discussion ("next steps")
with more detail on our future plans.
While that is so we are wary of promising too much at this point.

@@

> 4) We would be interested to see more of a discussion of the strengths and weakness of the various demographic inference methods.

We have added an additional paragraph to the discussion exploring various factors that may affect choice of inference method.
These include the data required by the method, the type of model, and the implementation.
We also provide a qualitative comparison between the performance of methods, as shown in our limited analysis.
We believe that a more comprehensive comparison between methods is beyond the scope of the current manuscript, which focuses on the resource itself, rather than its application.

@@

We thank the reviewer for bringing up this important point
and fully agree that the language in the manuscript needs to better emphasize the uncertainty in our current parameter estimates.
To address this, we have made several changes throughout the manuscript, including the passages cited above:

The first quoted passage now reads:
"For each organism, the catalog contains information on our current understanding of
the physical organization (e.g., chromosome structure) of its genome,
one or more inferred genetic maps (except for \textit{E.~coli}),
default population-level parameters (mutation rate and generation time estimates).
The catalog also contains numerous published demographic models for the first three species.
These available models and parameters are meant to represent the field's current understanding,
and we intend for this resource to evolve as new results become available."

The second passage now reads:
" Firstly, the library defines some basic information about our current understanding of each 
species' genome, including information about chromosome
lengths, average mutation rate estimates, and generation times.
We also provide access to detailed empirical information such as inferred genetic maps,
which model observed heterogeneity in recombination rate along chromosomes."

<!-- (The reviewer's suggestion is good, but we think that "current understanding"
conveys roughly the same meaning as "the latest reference genome" in less words,
and without making promises about genome assemblies.)

ADK commenting out-- don't think we need this
-->

@@

We made the suggested change:
"Importantly, we developed rigorous quality control methods to ensure that we have
correctly implemented the models as described in their original publication
and provide documented methods for others to contribute new models."

> 2. It would be wonderful to have a comments section for the models that would be either curated by a set of editors or crowd-sourced. I say this because over time, models will proliferate, and some will come to be regarded as out-of-date. One can imagine those approaching the field afresh will be overwhelmed by the possible selections and possible implement models that become outdated. If the goal is standardization, how do we communicate that standards change? A comment system (or even star-rating system?) may be wise to implement now. Assuming it can be layered on top of the existing structure, it may be enough for this publication to note this as a future challenge that needs development/addressing.

Thank you for this forward-thinking comment.
We considered various ways to do this
(e.g., by enabling the wiki associated with the github repository:
\url{https://github.com/popsim-consortium/stdpopsim/issues/415}),
but ended up deciding that (a) it's not yet clear what the right way to do this is,
and (b) it'll be significant work to do right that we aren't prepared to do at the moment.
Since we haven't encountered the problem of out of date models yet,
we feel happy about postponing this until the problem arises.

Moreover we believe that the issues feature on Github provides us with the current utility we need along these lines.

@@

> 3. In terms of the maturity of the examples developed for the initial release, I would have liked to see at least one simulation model with a selective sweep, one with background selection, and one with spatial stepping-stone structure. Each of these would be helpful test cases to implement to be sure that the existing catalog framework has the breadth/flexibility necessary to accommodate future use cases. I do not think this is a requirement for publication, but it would add great value to this initial release of the resource.

As mentioned in our response to the editor's comments, we agree that this is an important avenue to pursue in the near future.
However, performing adequate simulations with selection would require
a substantial amount of additional work and would likely distract from the current relatively simple focus
on inference of demographic history.
We definitely intend to include selection (and expand the available generic models) in future work,
as we now discuss in greater detail in the Discussion ("next steps").

> 4. Page 15. The approach of masking "low-recombination" portions of the chromosomes seems like an incomplete/indirect attempt to model the inherent limitations of sequencing to an "accessible" genome.
> a. Shouldn't the approach instead be to drop "low complexity" regions (e.g., as defined by an excessive number of "N"'s in the reference, low mapability scores, or via tools like RepeatMasker?). This part of the pipeline seems open to refinement.

Our initial motivation for masking was to reduce the overrepresentation of marginal trees with little to no recombination from biasing patterns of diversity in such a way that demographic inference methods would be misled. While we agree with the reviewer that different masking approaches might better reflect the masking done on real genomic data, at this time the best way to mask remains an open question, and we feel that a nuanced analysis of masking is outside the scope of this paper. For these reasons, we feel that masking using a simple recombination rate threshold is the most appropriate approach.
We note that their is however a substantial correlation between recombination rate and mapability (by any of the measures mentioned above) wherein the notoriously difficult portions of genomes to assemble are generally in regions of low recombination.
 We agree that there may indeed be better ways to mask, which is why we allow users to mask their simulations as they see fit.

@@

> b. Are the "masks" a separate configuration file for the simulations? It seems that it would be preferable for them to be separate from the recombination rate files - right now it reads as if the mask applied is a function of the genetic map file, but this seems too inflexible for users who prefer an alternative approach to masking.

Mask files are not currently a component of `stdpopsim` proper, rather they were implemented separately from running `stdpopsim`, for the sole purpose of comparing demographic inference methods. All of the masks that we have used are available on the `Analysis` repo that is associated with this manuscript. Users who download `stdpopsim` will always be simulating raw and unmasked tree sequence files, to which they can apply any variety of masks *post hoc*, if they so choose.

@@

> 1. Is the provenance information only provided if msprime is used to produce tree sequence files? Is a similar functionality in place with the SLiM back-end?

SLiM also records sufficient information to reconstruct the simulation in the tree sequence provenance
(including the software version, random seed, and a copy of the simulation script).

> 2. Little detail is given on the system of identifiers/versioning for models, maps, etc.

True, but the details are rather pedantic and we feel not material for the  manuscript.
We provide a link to our extensive documentation where we describe the system in detail.

@@

> 3. In the abstract, it's left vague what the nature of the resource is.
>
> a. The resource is described as an open source project and a catalog, but the fact that it's a web repository that contains a set of configuration files might be helpful to say explicitly.
> b. Also, while I wouldn't normally include url to software in an abstract, in this special case it seems like it could be very helpful to readers who want to jump right to the resource quickly?

Good point - we've clarified the nature of the resource,
but haven't included the URL since googling "stdpopsim" features the correct page as the top hit.

> 4. Page 3: "bespoke simulations":
>
> a. "bespoke" struck me as a distracting word choice, given its contemporary associations. Upon checking a dictionary, I see how it is an appropriate and precise word choice, but maybe it's best to instead simply say: "custom" or "one-off".
> b. To elaborate on the point you're making here, you could also share how the general modus operandi often includes the pasting of long unwieldy command-line calls for generating simulations into methods sections. Many of these command-line values are buried across the literature, often in supplementary methods. Additional virtues of your catalog is having: 1) a central repository for such models, and 2) modular configuration files (e.g. I can keep the same demographic model, but change the recombination map, without having to re-write, or learn, the innards of a complex command-line for ms/msprime)

We've replaced "bespoke" with "coded from scratch", which we think is more descriptive.
We hope that the other points are made elsewhere.

@@

> 7. Page 8. I like the approach of showing inverse coalescent rates, but it would be instructive to practitioners and useful for teaching, if in all figures you showed both the census sizes (e.g. with light grey dashed lines) and inverse rates (e.g. with dark grey solid lines as now in Fig 2).

First, we note that we decided to avoid using "census size", and simply refer to it as the "simulated population size", as we realized the use of "census" here could be misleading (see below for further discussion). Regarding the main point raised by the reviewer, we agree that in the single-population analyses, it would be instructive to show both the simulated (census) population size and the inverse coalescence rates. We thus plotted the simulated population sizes against the inverse coalescence rate for the model used in Figure 2, and found that they were near identical. As a result, we decided to show this comparison in Supplementary Figure S1 and discuss this issue in the text without adding the simulated population sizes to the main figures (as they didn't appear to add much). Note that in the multi-population analyses, the inverse coalescence rate is less appropriate, because some of the inference methods used in these analyses model gene flow, and should therefore be able to recover the true simulated population sizes. We now clarify this in the text as well.

> 8. Figure 4.
> a. Confusing how in panels A and B time moves left to right, and in panel C time moves right to left.
> b. Also, the figure would be improved by showing with vertical lines the timing of the CEU/YRI divergence in the true model. (similar comments hold for Figures S4 and S5)

We agree that the orientation of this figure was confusing, and so have changed it as suggested. In addition, we had previously plotted divergence times here as vertical lines, however we felt that plotting it this way made the figure hard to read since there was a great deal of overlap between these lines and the N(t) lines on the figure, which was was especially difficult to read when including multiple replicates. Thus, we decided to depict the divergence times (simulated and inferred) in a separate panel in the bottom of the figure, to improve readability.

@@

Good point - we changed the wording here as follows:

"For each simulation
replicate, we performed 10 runs of dadi and fastsimcoal, checking to ensure that
each method reached convergence."

> 10. Page 31. This is all very nice. To save readers a step, could you include the command-line flag for how to have msprime output the coalescence rate function?

Thanks!
There is not a command-line flag for obtaining the coalescence rates,
but this is easily obtainable through the python API.
We've added a paragraph to the supplement explaining what methods to use.

@@

Thank you! We hope you are right.

## Minor comments:

> The authors mention the implementation of the SLiM package into stdpopsim, but I was unable to find any details of this either in the manuscript or on the readthedocs page. If this was indeed implemented, I would also like to see the authors add some tutorials/results of analyses based on SLiM simulated data.

As mentioned in our response to the editor's comment, we added a demonstration of the use of SLiM to the results (see "Simulation engines" section and Supplementary Figures S1 and S2).
This new analysis uses SLiM in neutral simulations to validate that it produces data that is consistent with data simulated under the coalescent.
Furthermore, we provide a rudimentary examination of the effects of population size down-scaling, which is a common practice used in forward simulations such as SLiM.

@@

> 1) The authors mention that SLiM can be used as an alternative backend, which would presumably allow for simulations with selection. Although I don't think an extensive comparison of selection methods is necessary for this paper, it would be ideal if the authors can give some idea of how this would work (example command line, etc). There are also a myriad of methods for detecting/quantifying selection, and these simulations are not consistent either.

As mentioned in our response to the editor's comment, we added a demonstration of the use of SLiM to the results (see "Simulation engines" section and Supplementary Figures S1 and S2).
See also our response to related comments made by Reviewers #1 and #2.

> 2) I like the inclusion of the "zigzag" history, as well as generic piecewise constant models and IM models (page 7). I wonder if these could be included in a separate section (not organism specific) in the documentation and software (and then in Table 1). Right now the zigzag model is under humans in the catalog.

This is an interesting idea. We have added suite of generic models to stdpopsim that do not necessarily capture demographic parameters from a certain species,
but do reflect general trends observed in inference. The "zigzag" model could definitely be one of these, and indeed was initially implemented as a generic. However the reason we settled on the zigzag model is being defined as a human model is that its
effective population size values are taken from (or at least inspired by) values inferred from human genomes. To see our internal discussion of these issues from September 2019 please see this [closed issue](https://github.com/popsim-consortium/stdpopsim/issues/106).

@@

> -Figure 3 caption: wrong citation, should be Sheehan and Song

The citation was for the genetic map, but we've added the citation to Sheehan and Song for the model (also in the caption of Figure 2).

> -Page 10, last sentence before "Multi-population demographic models" section: clarify what "this setting" is (both species I assume)

We made the following change:  
"Accuracy is mixed among methods when doing inference on simulated data from these _D. melanogaster_
and _A. thaliana_ models, and generally worse than what we
observe for simulations of the human genome."

### 2020-05-14 popSimManu.tex
ADK final(?) pass on the manuscript

For these reasons, we have generated a standardized, community-driven resource
for simulating published demographic models from a number of popular study systems.
This resource, which we call \stdpopsim, makes running
realistic simulations for population genetic analysis a simple matter of
choosing pre-implemented models from a community-maintained catalog.
The \stdpopsim catalog currently contains six species: humans,
\textit{Pongo abelii},
\textit{Drosophila melanogaster}, \textit{Arabidopsis thaliana},
\textit{Escherichia coli}, and \textit{Canis familiaris}.
For each species, the catalog contains curated information on our current understanding of
the physical organization of its genome,
inferred genetic maps,
population-level parameters (e.g., mutation rate and generation time
estimates), and published demographic models.
These models and parameters are meant to represent the field's current understanding,
and we intend for this resource to evolve as new results become available, and
other existing models are added to \stdpopsim by the community.
We have implemented both a command line interface and a simple Python API
that can be used to simulate genomic data
from a choice of organism, genetic map, chromosome, and demographic history.
In this way, \stdpopsim will lower the barrier to high-quality simulation for exploratory analyses,
enable rigorous evaluation of population genetic software,
and contribute to increased reliability of population genetic inferences.

@@

The central feature of \stdpopsim is the species catalog, a systematic organization
of the key quantitative data needed to simulate a given species.
Data is currently available for humans,
\textit{P.~abelii},
\textit{D.~melanogaster}, \textit{A.~thaliana},
\textit{E.~coli}, and \textit{C.~familiaris}.
A species definition consists of two key elements.
Firstly, the library defines some basic information about our current understanding of each
species' genome, including information about chromosome
lengths, average mutation rate estimates, and generation times.
We also provide access to detailed empirical information such as inferred genetic maps,
which model observed heterogeneity in recombination rate along chromosomes.
Such maps are often large,
so we do not distribute them directly with the software, but make them available
for download in a standard format.
When a simulation using such a map is requested by the user,
\stdpopsim will transparently download the map data into a local cache,
% (\texttt{$\sim$/.local/cache/stdpopsim} by default on Unix platforms)
where it can be quickly retrieved for subsequent simulations.
In the initial version of \stdpopsim we support
the HapMapII~\citep{international2007second} and
deCODE~\citep{kong2010fine} genetic maps for humans;
the \cite{nater2017morphometric} maps for \textit{P.~abelii};
the \cite{salome2011recombination} map for \textit{A.~thaliana};
the \cite{comeron2012many} map for \textit{D.~melanogaster},
and the \cite{campbell2016pedigree} map for \textit{C.~familiaris}.
Adding further maps to the library is straightforward.
The second key element of a species description
within \stdpopsim is a set of carefully curated population genetic model
descriptions from the literature, which allow simulation under
specific historical scenarios that have been fit to present-day patterns of
genetic variation (See the Methods for a description of the community
development and quality-control process for these models.)
\renewcommand{\arraystretch}{1.2}
\begin{table}[t]
% Make sure the table is centered even though it's too wide
\makebox[\textwidth][c]{
    \begin{footnotesize}
    \input{model_table.tex}
    \end{footnotesize}
}
\caption{\label{tab:catalog}
Initial set of demographic models in the catalog and summary of computing resources needed for simulation.
For each model, we report the CPU time, maximum memory usage and the
size of the output \tskit file, as simulated using the \texttt{msprime}
simulation engine (version 0.7.4).
In each case, we simulate 100 samples
drawn from the first population, for the shortest chromosome of that species
and a constant chromosome-specific recombination rate.
The times reported are for a single run on an Intel i5-7600K CPU.
Computing resources required will vary widely depending on sample sizes, chromosome length,
recombination rates and other factors.
}
\end{table}

@@

%DRS: do we want to include these generic models in Table 1?

@@

Currently, \stdpopsim uses the  \texttt{msprime} coalescent simulator \citep{kelleher2016efficient}
as the default simulation engine.
Coalescent simulations, while highly efficient, are limited in their ability to model
continuous geography or
complex selection scenarios, such as recurrent sweeps and background selection.
For these reasons,
we have also implemented the forward-time simulator, \texttt{SLiM} \citep{haller2019tree,haller2019slim},
as an alternative backend engine to \texttt{stdpopsim}, allowing for the simulation of processes that cannot be modeled under
the coalescent. However, as forward-time simulators explicitly model all individuals in a population, simulating large
population sizes can be highly demanding of computational resources. One common practice used to address this challenge is to
simulate a \emph{smaller} population, but to rescale resulting times,
mutation rates, recombination rates, and selection coefficients
so that the intensity of mutation, recombination, and allele frequency change due to selection
per unit time remains the same
%% PLR: the following is not worded quite right, or at least confusingly, because if you scale time
%% then this scales rates also; I've opted for a less precise but more descriptive formulation?
% scale down the population size used in the simulations (\textit{N}),
% scale down times specified in the demographic model by the same factor, and scale up the mutation and recombination
% rates and selection coefficients such that the scaled parameters, \textit{N$\mu$}, \textit{Nr}, and \textit{Ns}, remain unchanged
\citep[see the \texttt{SLiM} manual and][]{uricchio2014robust}.
Our implementation of the \texttt{SLiM} backend allows easy use of this \emph{rescaling}
through a single ``scaling factor'' argument.
Such down-scaled simulations are not completely equivalent to simulating
all individuals in the population, and may lead to subtle differences,
especially in the presence of selection.
However, since many sequence-based measures of population diversity remain nearly unchanged when rescaling in this fashion,
this practice is effective for many purposes and widely employed.

@@

% ACS: there was indeed a lot of redundancy here.  DRS improved it a lot, but I've tried to do a bit more
\subsubsection*{ Single-population demographic models.}
For single-population demographic models, we compared
\MSMC~\citep{schiffels2014inferring}, \smcpp~\citep{terhorst2017robust}, and
\stairwayplot~\citep{liu2015exploring}
 on simulated genomes sampled from a single population,
under several of the demographic models described above.
However, these experiments raise the question of what to use as the ``true" population sizes in the case of multi-population models with migration.
In particular, a simple single-population model that is fit to data simulated
under a multi-population model,
is not expected to recover the actual simulated population sizes,
because of model misspecification.
Instead, we argue that the best one may expect in such a scenario is to infer a model that accurately reflects the
coalescence time distribution of the simulated model.
Under a multi-population model, the coalescence time distribution is influenced by migration between the target population and populations not analyzed in inference,
as well as by the ancestral effective population sizes.
The inverse coalescence rate is commonly interpreted as the effective population size,
since these are equal in a single-population model with random mating.
We thus analytically computed inverse coalescence
rates in \texttt{msprime} for each simulated model, and used them as benchmarks for the ``true'' effective population sizes.
See the Appendix for a precise definition and description of the inverse coalescence rate computation.

Figure \ref{fig:n_t_ragsdale} presents the results
from simulations under OutOfAfricaArchaicAdmixture\_5R19,
a model of human migration out of Africa that includes archaic admixture
\citep{ragsdale2019models}, along with an empirical genetic map. In each column of this figure
we show the inferred population size history (denoted $N(t)$)
from samples taken from each of the three extant populations in the model.
In each row we show comparisons among the methods (including two sample sizes for \MSMC).
Blue lines show estimates from each of three replicate whole genome simulations,
and black lines indicate the ``true" values depicted by the inverse coalescence rates (although in this specific model
the inverse coalescence rates are very close to the simulated population sizes;
Figure \ref{fig:census_vs_IRC}).
%DRS: trying to cut down on the redundancy between the coal rate stuff here and the previous paragraph
While there is variation in accuracy among methods, populations, and individual replicates,
the methods generally produce a good estimate
of the true effective population sizes of the simulations, with
inferred values mostly within a factor of two of the truth,
and most methods inferring a bottleneck at approximately the correct time.

@@

As most method development for population genetics has been focused on human
data, it is of consequence to ask how such methods might perform in non-human
genomes. Figure \ref{fig:n_t_sheehan} shows parameter estimates from the African3Epoch\_1S16
model, originally estimated from an African sample of \textit{D.~melanogaster} \citep{sheehan2016deep},
and Figure \ref{fig:n_t_AraTha} shows estimates from simulations of \textit{A.~thaliana}
under the African2Epoch\_1H18 model originally inferred by \cite{huber2018gene}.
In both cases, as with humans, we use \stdpopsim to simulate replicate genomes using an empirically-derived genetic map,
and try to infer back parameters of the simulation model.
Accuracy is mixed among methods when doing inference on simulated data from these \textit{D.~melanogaster}
and \textit{A.~thaliana} models, and generally worse than what we
observe for simulations of the human genome.

@@

Although these results do not represent an exhaustive benchmarking,
we have highlighted some of the strengths and weaknesses of these methods.
Future work should build on these results and undertake more in-depth comparisons
under a wider range of simulated demographic models.

@@

All methods for inferring demographic history have strengths and weaknesses \citep[as recently reviewed by][]{beichman2018review}.
We compared inferences from simulated whole genome data, but many factors affect choice of methodology.
Markovian coalescent methods (\MSMC and \smcpp) require long contiguous stretches of sequence data.
In contrast, frequency spectrum methods (\stairwayplot, \dadi, and \fastsimcoal) can use reduced-representation sequencing data, such as RADseq \citep{andrews2016radseq}.
\dadi and \fastsimcoal require a pre-specified parametric model, unlike \MSMC, \smcpp, and \stairwayplot.
Using a parametric approach yields less noisy results, but a model that is too simple may not capture important demographic events (Figures~\ref{fig:IM_popn_human} and~\ref{fig:two_popn_fly}),
and other forms of model misspeficification may also produce undesireable behavior.
From a software engineering perspective, methods also differ in their ease of installation and use.
We hope our workflows will assist in the application of all the methods we have considered.

@@

One of our goals is to engage research communities studying other taxa,
so as to expand the resource to many more species.
Although we have included demographic models and recombination maps,
there are many biological processes that we do not model.
Some of the additions that we are enthusiastic to add are:
selection (including distributions of fitness effects, maps of functional elements, and both single and recurrent hitchhiking events),
gene conversion, mutation models (rate heterogeneity),
more realistic demography (overlapping generations, separate sexes, mortality/fecundity schedules),
geographic population structure,
and downstream aspects of data quality (genotyping and mapping error).
Moreover, an in-depth investigation into the effects of population-size rescaling under many of the
above scenarios is warranted, given our preliminary findings using neutral simulations
(Figures \ref{fig:slim_val_map} and \ref{fig:slim_val_nomap}).
Some other important processes are more challenging to model with current simulation software,
such as
structural variation,
changing recombination maps over time,
transposable elements,
and context-dependent mutation.

>>>>

For these reasons, we have generated a standardized, community-driven resource
for simulating published demographic models from a number of popular study systems.
This resource, which we call \stdpopsim, makes running
realistic simulations for population genetic analysis a simple matter of
choosing pre-implemented models from a community-maintained catalog.
The \stdpopsim catalog currently contains six species: humans,
\textit{Pongo abelii}, \textit{Canis familiaris},
\textit{Drosophila melanogaster}, \textit{Arabidopsis thaliana},
and \textit{Escherichia coli}.
For each species, the catalog contains curated information on our current understanding of
the physical organization of its genome,
inferred genetic maps,
population-level parameters (e.g., mutation rate and generation time
estimates), and published demographic models.
These models and parameters are meant to represent the field's current understanding,
and we intend for this resource to evolve as new results become available, and
other existing models are added to \stdpopsim by the community.
We have implemented both a command line interface and a simple Python API
that can be used to simulate genomic data
from a choice of organism, genetic map, chromosome, and demographic history.
In this way, \stdpopsim will lower the barrier to high-quality simulation for exploratory analyses,
enable rigorous evaluation of population genetic software,
and contribute to increased reliability of population genetic inferences.

@@

The central feature of \stdpopsim is the species catalog, a systematic organization
of the key quantitative data needed to simulate a given species.
Data is currently available for humans,
\textit{P.~abelii}, \textit{C.~familiaris},
\textit{D.~melanogaster}, \textit{A.~thaliana},
and \textit{E.~coli}.
A species definition consists of two key elements.
Firstly, the library defines some basic information about our current understanding of each
species' genome, including information about chromosome
lengths, average mutation rate estimates, and generation times.
We also provide access to detailed empirical information such as inferred genetic maps,
which model observed heterogeneity in recombination rate along chromosomes.
Such maps are often large,
so we do not distribute them directly with the software, but make them available
for download in a standard format.
When a simulation using such a map is requested by the user,
\stdpopsim will transparently download the map data into a local cache,
% (\texttt{$\sim$/.local/cache/stdpopsim} by default on Unix platforms)
where it can be quickly retrieved for subsequent simulations.
In the initial version of \stdpopsim we support
the HapMapII~\citep{international2007second} and
deCODE~\citep{kong2010fine} genetic maps for humans;
the \cite{nater2017morphometric} maps for \textit{P.~abelii};
the \cite{campbell2016pedigree} map for \textit{C.~familiaris};
the \cite{salome2011recombination} map for \textit{A.~thaliana};
and the \cite{comeron2012many} map for \textit{D.~melanogaster}. 
Adding further maps to the library is straightforward.
The second key element of a species description
within \stdpopsim is a set of carefully curated population genetic model
descriptions from the literature, which allow simulation under
specific historical scenarios that have been fit to present-day patterns of
genetic variation (See the Methods for a description of the community
development and quality-control process for these models.)
\renewcommand{\arraystretch}{1.2}
\begin{table}[t]
% Make sure the table is centered even though it's too wide
\makebox[\textwidth][c]{
    \begin{footnotesize}
    \input{model_table.tex}
    \end{footnotesize}
}
\caption{\label{tab:catalog}
Initial set of demographic models in the catalog and summary of computing resources needed for simulation.
For each model, we report the CPU time, maximum memory usage and the
size of the output \tskit file, as simulated using the \texttt{msprime}
simulation engine (version 0.7.4).
In each case, we simulate 100 samples
drawn from the first population, for the shortest chromosome of that species
and a constant chromosome-specific recombination rate.
The times reported are for a single run on an Intel i5-7600K CPU.
Computing resources required will vary widely depending on sample sizes, chromosome length,
recombination rates and other factors.
}
\end{table}

@@

%DRS: do we want to include these generic models in Table 1?
%ADK: not a bad idea...

@@

Currently, \stdpopsim uses the  \texttt{msprime} coalescent simulator \citep{kelleher2016efficient}
as the default simulation engine.
Coalescent simulations, while highly efficient, are limited in their ability to model
continuous geography or
complex selection scenarios, such as recurrent sweeps and background selection.
For these reasons,
we have also implemented the forward-time simulator, \texttt{SLiM} \citep{haller2019tree,haller2019slim},
as an alternative backend engine to \texttt{stdpopsim}, allowing for the simulation of processes that cannot be modeled under
the coalescent. However, as forward-time simulators explicitly model all individuals in a population, simulating large
population sizes can be highly demanding of computational resources. One common practice used to address this challenge is to
simulate a \emph{smaller} population, but to rescale resulting times,
mutation rates, recombination rates, and selection coefficients
so that the intensity of mutation, recombination, and allele frequency change due to selection
per unit time remains the same
%% PLR: the following is not worded quite right, or at least confusingly, because if you scale time
%% then this scales rates also; I've opted for a less precise but more descriptive formulation?
% scale down the population size used in the simulations (\textit{N}),
% scale down times specified in the demographic model by the same factor, and scale up the mutation and recombination
% rates and selection coefficients such that the scaled parameters, \textit{N$\mu$}, \textit{Nr}, and \textit{Ns}, remain unchanged
\citep[see the \texttt{SLiM} manual and][]{uricchio2014robust}.
Our implementation of the \texttt{SLiM} backend allows easy use of this \emph{rescaling}
through a single ``scaling factor'' argument.
Such down-scaled simulations are not completely equivalent to simulating
all individuals in the population, and may lead to subtle differences,
especially in the presence of selection.
However, since many sequence-based measures of population diversity remain nearly unchanged when rescaling in this fashion,
this practice is effective for many purposes and widely employed.
%ADK: I think we need a citaiton above for scaling. Maybe https://doi.org/10.1534/genetics.113.156935

@@

\subsubsection*{ Single-population demographic models.}
For single-population demographic models, we compared
\MSMC~\citep{schiffels2014inferring}, \smcpp~\citep{terhorst2017robust}, and
\stairwayplot~\citep{liu2015exploring}
 on simulated genomes sampled from a single population,
under several of the demographic models described above.
However, these experiments raise the question of what to use as the ``true" population sizes in the case of multi-population models with migration.
In particular, a simple single-population model that is fit to data simulated
under a multi-population model,
is not expected to recover the actual simulated population sizes
because of model misspecification.
Instead, we argue that the best one may expect in such a scenario is to infer a model that accurately reflects the
coalescence time distribution of the simulated model.
Under a multi-population model, the coalescence time distribution is influenced by migration between the target population and populations not analyzed in inference,
as well as by the ancestral effective population sizes.
The inverse coalescence rate is commonly interpreted as the effective population size,
since these are equal in a single-population model with random mating.
We thus analytically computed inverse coalescence
rates in \texttt{msprime} for each simulated model, and used them as benchmarks for the ``true'' effective population sizes.
See the Appendix for a precise definition and description of the inverse coalescence rate computation.

Figure \ref{fig:n_t_ragsdale} presents the results
from simulations under OutOfAfricaArchaicAdmixture\_5R19,
a model of human migration out of Africa that includes archaic admixture
\citep{ragsdale2019models}, along with an empirical genetic map. In each column of this figure
we show the inferred population size history (denoted $N(t)$)
from samples taken from each of the three extant populations in the model.
In each row we show comparisons among the methods (including two sample sizes for \MSMC).
Blue lines show estimates from each of three replicate whole genome simulations,
and black lines indicate the ``true" values depicted by the inverse coalescence rates (although in this specific model
the inverse coalescence rates are very close to the simulated population sizes;
Figure \ref{fig:census_vs_IRC}).
While there is variation in accuracy among methods, populations, and individual replicates,
the methods generally produce a good estimate
of the true effective population sizes of the simulations, with
inferred values mostly within a factor of two of the truth,
and most methods inferring a bottleneck at approximately the correct time.

@@

As most method development for population genetics has been focused on human
data, it is important to ask how such methods might perform in non-human
genomes. Figure \ref{fig:n_t_sheehan} shows parameter estimates from the African3Epoch\_1S16
model, originally estimated from an African sample of \textit{D.~melanogaster} \citep{sheehan2016deep},
and Figure \ref{fig:n_t_AraTha} shows estimates from simulations of \textit{A.~thaliana}
under the African2Epoch\_1H18 model originally inferred by \cite{huber2018gene}.
In both cases, as with humans, we use \stdpopsim to simulate replicate genomes using an empirically-derived genetic map,
and try to infer back parameters of the simulation model.
Accuracy is mixed among methods when doing inference on simulated data from these \textit{D.~melanogaster}
and \textit{A.~thaliana} models, and generally worse than what we
observe for simulations of the human genome.

@@

Although these results do not represent an exhaustive benchmarking,
we have begun to highlight some of the strengths and weaknesses of these methods.
Future work should build on these results and undertake more in-depth comparisons
under a wider range of simulated demographic models.

@@

All methods for inferring demographic history have strengths and weaknesses \citep[as recently reviewed by][]{beichman2018review}.
We compared inferences from simulated whole genome data, but many factors affect choice of methodology.
Markovian coalescent methods (\MSMC and \smcpp) require long contiguous stretches of sequence data.
In contrast, frequency spectrum methods (\stairwayplot, \dadi, and \fastsimcoal) can use reduced-representation sequencing data, such as RADseq \citep{andrews2016radseq}.
\dadi and \fastsimcoal require a pre-specified parametric model, unlike \MSMC, \smcpp, and \stairwayplot.
Using a parametric approach yields less noisy results, but a model that is too simple may not capture important demographic events (Figures~\ref{fig:IM_popn_human} and~\ref{fig:two_popn_fly}),
and other forms of model misspecification may also produce undesirable behavior.
From a software engineering perspective, methods also differ in their ease of installation and use.
We hope our workflows will assist in the application of all the methods we have considered.

@@

One of our goals is to engage research communities studying other taxa,
so as to expand the resource to many more species.
Although we have included demographic models and recombination maps,
there are many biological processes that we do not model.
Some of the additions that we are enthusiastic to add are:
selection (including distributions of fitness effects, maps of functional elements, 
both single and recurrent hitchhiking events, and selection on polygenic traits),
gene conversion, mutation models (rate heterogeneity),
more realistic demography (overlapping generations, separate sexes, mortality/fecundity schedules),
geographic population structure,
and downstream aspects of data quality (genotyping and mapping error).
Moreover, an in-depth investigation into the effects of population-size rescaling under many of the
above scenarios is warranted, given our preliminary findings using neutral simulations
(Figures \ref{fig:slim_val_map} and \ref{fig:slim_val_nomap}).
Some other important processes are more challenging to model with current simulation software,
such as
structural variation,
changing recombination maps over time,
transposable elements,
and context-dependent mutation.

% note: this is addressing reviewer comments about model uncertainty
We wish to emphasize that although the included demographic histories are some of the
most widely used models for our current set of species,
we anticipate the set of available models to expand
as new methods and new modeling frameworks are developed.
For instance, the current models all describe a small set of discrete, randomly mating populations,
which are likely good approximations for deep-time population history,
but may be less useful for methods describing dynamics of contemporary populations.
\Stdpopsim's framework is sufficiently general that more realistic population models
will be easily incorporated, as they are published.

%ADK: I cut this off here-- I think thais is a fine ending

%Our current set of models is not exhaustive at this point however,
%and othercan be readily incorporated into \stdpopsim.
%Additional complications such as changing
%genome builds as assemblies improve must also be incorporated.
%As the collection of models and species grows, we hope to
%incorporate crowd-sourced community input
%to highlight the most appropriate models and genome annotations.
%DRS: not in love with the word "annotations" here as some might think we are talking gene annotations (which we will be eventually but not yet), but "details" is too vague.
